CLPFUDatabase: A suite of R packages for energy conversion chain analysis

### 2023-12-20 paper.Rmd
Add a blank line.

# (3) Run the PFUDatabase pipeline to create RUVY matrices.
targets::tar_make_future(
  script = file.path("ExampleFolder", "_targets_pfudatabase.R"), 
  workers = 4
)
# (4) Run the PFUAggDatabase pipeline to aggregate 
#     energy and calculate efficiencies.
targets::tar_make_future(
  script = file.path("ExampleFolder", "_targets_pfuaggdatabase.R"),
  workers = 4
)
```

>>>>

# (3) Run the PFUDatabase pipeline to create RUVY matrices.
targets::tar_make_future(
  script = file.path("ExampleFolder", "_targets_pfudatabase.R"), 
  workers = 4
)

# (4) Run the PFUAggDatabase pipeline to aggregate 
#     energy and calculate efficiencies.
targets::tar_make_future(
  script = file.path("ExampleFolder", "_targets_pfuaggdatabase.R"),
  workers = 4
)
```
